---
name: Robby
surname: De Pauw
profilepic: robby_240.jpeg
position: "Senior Researcher, Statistican, Epidemiologist"
address: ""
phone: +32 (0) 499 61 59 72
www: robbydepauw.be
email: "robby@twrite.be"
twitter: RobbyDePauw
github: rdpauw
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# General information

* **Name:** Robby De Pauw
* **Date of Birth:** 25/07/1990
* **Place of Birth:** Asse
* **Nationality:** Belgian
* **Private adress:** Weversstraat 28, 9000 Ghent


# Education

```{r}
orcid_edu
```

# Additional courses

```{r}
add_edu
```

# Professional experience

```{r}
pro
```

# Publications

```{r}
bibliography_entries("works.bib")
```

\newpage

# Projects

```{r}
projects
```

# PhD

```{r}
phd
```

# Teaching

```{r}
teach
```

\newpage

# Presentation (first author)

```{r}
presentation
```

# Memberships and associations

```{r}
member
```

# International stays

```{r}
int_stays
```

\newpage

# Master theses

```{r}
master_theses
```


\newpage

# Professional skills

## Programming and Statistics

```{r, out.width='50%'}
stat_fig
```

## Languages

\begin{table}[h]
\begin{tabular}{@{}llll@{}}
\toprule
Language & Reading & Speaking & Writing \\ \midrule
Dutch    & +++++   & +++++    & +++++   \\
English  & +++++   & +++++    & +++++   \\
French   & ++++    & +++      & ++++    \\
German   & ++     & +        & +       \\ \bottomrule
\end{tabular}
\end{table}

